Kindly Bent to Free Us

### 2019-07-04 kindly/motivation.tex
explanation array api

We distinguish several kinds of operation: constructors, destructore,
observers, and mutators. 
Constructors and destructors like \lstinline/create/ and \lstinline/free/ manipulate the whole
array. As with channels in \cref{sec:session-linearity},
\lstinline/create/ yields a linear resource which is consumed by \lstinline/free/.
During the lifetime of the array resource \lstinline/a/, we can split
off \emph{immutable borrows} \lstinline/&a/ that provide a read-only
view or \emph{mutable borrows} \lstinline/&!a/ for read-write views.
Observer functions such as \lstinline/get/ expect an immutable borrow
argument, mutator functions such a \lstinline/set/ expect
a mutable borrow.

@@

@@

  val get : ('a : un) => &('a t) * int -> 'a
  val set : &!('a t) * int * 'a -> unit

>>>>

The intention of this API is to enable arrays to contain affine
elements. One would first use \lstinline/create n v/ to create
an (unrestricted) array of size \lstinline/n/ with some value
\lstinline/v/. This value must be unrestricted as it is duplicated to
initialize all array elements. Using the \lstinline/map/ function we
can transform the unrestricted elements into linear affine)
ones. This transformation yields a linear (affine) array that can be
processed further using \lstinline/map/ (or \lstinline/set/ if
affine). Before \lstinline/free/ing the array the elements must be
affine, again.

We distinguish several kinds of operation: constructors, destructore,
observers, and mutators. 
Constructors and destructors like \lstinline/create/ and \lstinline/free/ manipulate the whole
array. As with channels in \cref{sec:session-linearity},
\lstinline/create/ yields a linear resource which is consumed by \lstinline/free/.
During the lifetime of the array resource \lstinline/a/, we can split
off \emph{immutable borrows} \lstinline/&a/ that provide a read-only
view or \emph{mutable borrows} \lstinline/&!a/ for read-write views.
Observer functions such as \lstinline/length/ and \lstinline/get/ expect an immutable borrow
argument, mutator functions such a \lstinline/set/ expect
a mutable borrow.

@@

  val create : ('a : un) => int -> 'a -> 'a t
  val free : ('a : aff) => 'a t -> unit

@@

  val get : ('a : un) => &('a t) * int -> 'a
  val set : ('a : aff) => &!('a t) * int * 'a -> unit
